\documentclass[12pt]{article}

  \author{}
  \date{}
  \title{The Mondoblack Blackmarket\vspace{-4ex}}

  \usepackage{avant}
  \usepackage{verse}


  \newcommand{\attrib}[1]{%
  \nopagebreak{\raggedleft\footnotesize #1\par}}
  \renewcommand{\poemtitlefont}{\normalfont\large\itshape\centering}

\begin{document}
\maketitle

We turned the corner on street where we were meeting Susan
and David, we were releaved that the little coffee shop wasn't too
busy. Think we past the morning rush and could have our pick of
their nice outdoor seating and views of the pretty street. The
coffee shop and surrounding area had been growing a thriving arts
community for quite some time now and it a good vibe and lots to
see and do. As I was looking around, while Kathy was chatting with
the hostess, my eye caught a new display of colored glass right in
middle of the walkway a few doors down. It was making some
interesting patterns on the sidewalk that my mind was trying to
recognize and interpret. That was when Kathy nudged me a little,
``Saul, table's ready.'' She smiled, ``Were you spacing off
again?'' ``Maybe a little.'' I hinted with a slight smile. I made
a note to investigate the new artwork next time I was in the area.
The patterns weren't completely geometrical or symmetrical but
there was a mathematical quality to them I couldn't fully discern.

We took our seats and I ordered my usual black coffee to start and
Kathy, always loving variety felt like tomato juice that morning.
``Not sure why I'm craving TJ but it just sounds good today.'',
she said. I thought about the coffee here, it has always been the
best, better than any big chain, better than an expensive machine
at home. Asked the owner about it once and he smiled and said, ``I
run a coffee shop, because that's what I've always loved; a
\emph{good} cup of coffee. Now I get to share it with other people
who know quality and now my life is full of quality friends and
customers.'' He grinned big, ``Pretty good deal 'eh?'' I
definitely agreed. He continued, ``But really I got lucky with
this location. I can charge \$5 for a muffin and then have enough
left over to pay for the good stuff.'' I knew he meant his famous
coffee.

As the server was returning, Susan and David appeared on the
sidewalk. Susan was Kathy's little sister, she's been working hard
in medical school and just finished some major exam so it was
great she could come out with us rather than her usual regime of
study and school. David, her fiance, supported her both
emotionally and financially in her studies. He was a nice guy,
sometimes too nice I thought as Kathy was more driven. But they
both had said that it's her turn first and then David will get to
further his career by getting some advanced electrician
certifications. 

''So what's this show all about?'' Susan asked. Her driven nature
hadn't fully caught up with the fact that school was over for now
and she could relax more.  They probably had some other plans that
day: hopefully to rekindle and reconnect in their relationship
together during the short reprive before other responsibilities
assert themselves. Kathy started to explain, ``It's a mix of new
technology art. Saul helped setup the network and worked with some
of the artists to make sure they had the internet connectivity and
helped with troubleshooting some of the displays.'' I continued,
``There are some interesting pieces using all kinds of different
technology; newer tablets, old CRTs, wireless, bluetooth, etc.
Think you guys will like it.  I was hoping it wouldn't be all low
voltage so I could have thrown some work to David.''  He smiled,
``Oh man, thanks for thinking of me, that's why you're my favorite
brother-in-law.  But work is going good right now, we're all
pretty busy at the job site.  Going to be getting some good OT the
next month or two. Maybe we can plan a vacation together next year
during Kathy's long break?'' We all thought it was a great idea. I
made a note to bring it up casaully in the next few months in
hopes it would happen. 


We finished eating and David and I both got coffees to go. We each
took sips and nodded in agreement, good coffee. The art show was a
couple of blocks away. The sun was out and it was turning out to
be a great spring day. The show shouldn't be too busy as the nice
weather will keep a lot people outside. I liked it that way so you
had more time to check the pieces out. Just sitting and looking at
the images without trying to make sense of it right away seemed to
help make a different kind of sense of the art. We wondered the
different pieces, it was a smaller gallery but with three good
sized rooms.


Off to the side of one of the rooms was just a door frame standing
a couple of feet from the wall. It was labeled
Mondoblack\copyright and a little label on the handle said ``Pull
here''.  ``Huh, don't remember this piece when I was helping
setup.'', I said. Remarking on its simplicity, ``Really not much
too it so the could've brought it in this morning.'',  I thought
it was a little trite, it looked a like the door from the
introduction of the old Twilight Zone television show. Kathy spoke
up, ``Oh, I did hear about this one, mainly because
Mondoblack\copyright is
copyrighted and you need to obtain a license to use it in any way.
It's some new material scientists created with nanotubes I think
and is pretty expensive and difficult to make in any large
quantity. And like the name suggests it's, um, really black.'' We
chuckled. ``So who wants to open the door?'' Susan asked. We
looked at each other and all shrugged. ``Okay, I'll do it'' I
said. 

Slowly I pulled the door open and saw the flatest darkest black
I've ever seen with the lights on. We all stepped back to let the
door fully open and to allow everyone a view. It was a little
disconcerting looking into the doorway.  Like your eyes had
nothing to pin to, it was totally flat and two dimensional. I
walked to the side so I could see it from more on an angle inside
its frame. But even then it just looked so flat, like an optical
illusion of some sort. As I continued to the back of the door
frame it was just painted white. Just a sheet of plywood that was
painted with the Mondoblack\copyright on the side facing the door and
white on the back. There was some small black writing in the middle of the
back of the door:
\settowidth{\versewidth}{This an average line i think}
\begin{verse}
  Cut doors and windows for a room; \\
  It is the empty spaces which make it useful. \\
\end{verse}
\attrib{Lao Tzu, The Tao Te Ching}


I continued around to join the others and see what they thought
about it. ``Um, it's kinda cool but seems too simple.'', David said. ``I mean,
yeah, it's really black, and I keep looking for some blemish or
light but there's nothing there and it looks so flat, kind of
boring once you look at it a bit.'' he continued. 

\end{document}
