\documentclass[12pt]{article}

  \title{The Mondoblack Black Market Outline}
  \author{Thomas Enderlin\vspace{-2ex}}
  \date{}

  \usepackage{outlines}  % Outline
	\usepackage{mathpazo}  % Palatino font
  \usepackage{verbatim}  % Comments

\begin{document}
\maketitle
\begin{outline}[enumerate]
  \1 Main Characters
    \2 Paul.  NT temperament. Main character
      \3 Married to Karen. Geeky. Used to work in IT. Dry sense
      of humor. Conflicts, in good fun, with Susan.
    \2 Karen. NF temperament. Paul's wife is a nurse
      \3 Emphatic, caring, compassionate
    \2 Susan. SP temperament. Karen's sister is a home maker, socialite
      \3 Sensor, outgoing, extroverted, social, talkative,
      gossips, impulsive, gregarious
    \2 David. SJ temperament. Susan's husband. Electrician.
      \3 Sensor, confident, team player, like sports, blue
      collar

  \1 Secondary characters
  \2 Hal : coffee shop manager
  \2 Jan : hostess
  \2 Dan : David's old boss
  \2 Zeke : football player, Dan's teenage son
  \2 Tony : Zeke's friend
  \2 Tyler : football player, Zeke's rival
  \2 Caleb : Tyler's friend


\1 Introduction
  \2 Main characters meet at coffee shop
    \3 introduce personalities
  \2 secondary characters
    \3 Hal. Owner of coffee shop
    \3 Jan. Hostess. Older woman
  \2 Describe co-op businesses and neighborhood
  \2 Introduce AI, AR, VR
  \2 Discuss art show

\1 Art Show
  \2 Introduce main theme. Mondoblack
    \3 Blackest substance ever created. 
    \3 Represents emptiness, the abyss, the unknown. Nihilism.
    \3 Contains both possibility of treasure (creation) and dissolution (destruction)
    \3 Women are repelled due to the possibility of destruction.
    Goes against their archetypes of the mother, child and
    family.
    \3 Men are attracted to the unknown, the possibility of
    returning with treasure, the power of security and creation. Goes
    with their archetype of the hero.
  \2 Initial impressions of characters
  \2 Post-show discussion of other pieces
  \2 Paul has a dream that night about the vast emptiness and at
  its heart, its center, some light, a possibility of a way out.

\1 Art robbery
  \2 Paul wakes up, takes walk in the dark and passes robbers.
  \2 Teenager scene. Characters are all part of football team
    \3 Zeke. Son of David's old boss. Narcissistic asshat
    character. Pushy, obnoxious, acts tough and domineering.
    \3 Tony. Zeke's friend. Big and dumb, but really kind, a
    gentle giant. Controlled and taken advantage by Zeke and by
    his own family.
    \3 Tucker or Tyler? Competes with Zeke. More well adjusted
    and honorable.
    \3 Caleb. Tyler's friend. Smart and nerdy. Skinny, a runner.
    Protected by Tyler.
    \3 Girls??? I think yes. Two of them.
    \3 Abby. Zeke's girlfriend, but is now interested in Tyler.
    Resentful that Tyler isn't interested in her because she's a
    harpy cunt. Likes the extra attention Zeke gives her and the
    aggressiveness he displays when she flirts with other boys.
    \3 Chloe. Interested in Caleb. Also is smart and sees
    Caleb's potential. Abby is popular and is why she hangs out
    with her. 
  \2 Scene ends with Caleb and Tyler both looking at Mondoblack.

\1 Evening pool party
  \2 Situated in the house of David's old boss, Danny, who is
  Zeke's father.
  \2 News of catatonic kids at the hospital, Caleb and Tyler.
  \2 Paul has experience in pool.
    \3 AR/AI truth session.

\1 Morning after, conclusion?
  \2 Visit co-op farm stand. Couple who run it are Chloe's
  parents. Discuss seeding/planting. Farm and food (culinary)
  classes for girls, maybe?
  \2 News about kids and the term Mondoblack black market
    \3 Nationwide robberies. More catatonic kids (boys).
    \3 Discussion?
    \3 Interview one of the thieves?
  \2 Paul is done at hydro farm. Goes to coffee shop. Shop is very full and sits with a Buddhist monk
    \3 Monk tells him he is visiting the Mondoblack art show.
    \3 Wants to contemplate and meditate on the usefulness or
    utility of emptiness
    \3 Gives analogy of empty cup
    \3 Finishes with equation: the limit of usefulness is
    reached as emptiness approaches its maximum 
  \2 Story ends
    \3 Paul's cup is empty and (new) waitress comes by and asks
    him if he would like coffee. Yes. Would like cream and
    sugar? Paul looks at his empty cup. Looks at the waitress
    and smiles. ``No thank you. I like it black.''

\end{outline}
\end{document}


